Active-contours driven registration applied in the correction of susceptibility-derived distortions of diffusion MR images

### 2015-04-06 Publications/2015-NeuroImage/04-methods.tex
add ISBI reference

The general experimental framework for the real datasets is presented in \autoref{fig:evworkflows}.
We designed the workflow with based on two arbitrary decisions:
First, we map $\gammaset_R$ into a bivariates image comprising the \gls*{fa} and the
  \gls*{adc} maps derived from the distorted \gls*{dmri} dataset.
Previous studies \citep{ennis_orthogonal_2006,}
The underlying segmentation model \omegaset{}
Selecting the appropriate labels in the \emph{aparc} segmentation, we applied
  \texttt{mri\_tessellate} to extract the surface of the following
  six homogeneous regions $\Omega_l$:
  1) the thalamus, $\Omega_{Tha}$;
  2) \gls*{csf} of the ventricular system and deep \gls*{gm} structures, $\Omega_{VdGM}$;
  3) cerebral \gls*{wm}, $\Omega_{WM}$;
  4) brain stem and cerebellar \gls*{wm}, $\Omega_{bst}$;
	5) cerebellar \gls*{gm}, $\Omega_{cbGM}$; and
	6) cortical \gls*{gm} surface, $\Omega_{pial}$.
The segmentation model corresponding to this selection of surfaces is presented in
  \autoref{fig:model}, and further addressed in \autoref{sec:res_model_and_metric}.

>>>>

The general experimental framework for the real datasets is presented in \autoref{fig:evworkflows}.
\citep{esteban_brain_2012}

We designed the workflow with based on two arbitrary decisions:
First, we map $\gammaset_R$ into a bivariate image comprising the \gls*{fa} and the
  \gls*{adc} maps derived from the distorted \gls*{dmri} dataset.
In a previous study
The underlying segmentation model \omegaset{}
Selecting the appropriate labels in the \emph{aparc} segmentation, we applied
  \texttt{mri\_tessellate} to extract the surface of the following
  six homogeneous regions $\Omega_l$:
  1) the thalamus, $\Omega_{Tha}$;
  2) \gls*{csf} of the ventricular system and deep \gls*{gm} structures, $\Omega_{VdGM}$;
  3) cerebral \gls*{wm}, $\Omega_{WM}$;
  4) brain stem and cerebellar \gls*{wm}, $\Omega_{bst}$;
	5) cerebellar \gls*{gm}, $\Omega_{cbGM}$; and
	6) cortical \gls*{gm} surface, $\Omega_{pial}$.
The segmentation model corresponding to this selection of surfaces is presented in
  \autoref{fig:model}, and further addressed in \autoref{sec:res_model_and_metric}.
